preprocess_sketches THU

### 2022-07-21 analysis/step1_get_drawings/THU_Drawings/preprocess_sketches.Rmd
reorg get drawings folder to add scripts to get svg strokes

# copy included drawings/tracings and rename
```{r}
file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(compiled_dataset_path, drawings_to_include$better_filename))
```

```{r}
file.copy(fs::path(drawing_path, tracings_to_include$fullPath), fs::path(compiled_tracing_dataset_path, tracings_to_include$better_filename))
```

>>>>

# copy included drawings/tracings and rename
```{r}
recopy=FALSE
if (recopy){
file.copy(fs::path(drawing_path, drawings_to_include$fullPath), fs::path(compiled_dataset_path, drawings_to_include$better_filename))
}
```

```{r}
if (recopy){
file.copy(fs::path(drawing_path, tracings_to_include$fullPath), fs::path(compiled_tracing_dataset_path, tracings_to_include$better_filename))
}
```
